Our best attempt at fixing the internet

### 2013-11-28 paper.tex
Basic additions

\section{Introduction}
\section{The {\secit Body} of The Paper}
\section{Conclusions}

@@

\begin{appendix}

\section{Final Thoughts}

>>>>

\section{Introduction}

Attempt to build a safer internet.

We want it to be compatible with our actual infrastrucure and on the machines that are now on the field.

Our threat model assumes that any wire can be tapped. No connection is safe. Source IP spoofing.

\section{Addressage security}

Introduce current system. Domain name registrars, DNS ...

\subsection{ Issues with the current system} 
Zooko's triangle
\subsection{How to fix it}
\subsubsection{Certificate Pinning}
Works great but not scalable - first fix.
\subsubsection{DANE}
Works great but still having a centralized registry / domain registrars
DNSSec
\subsubsection{Tor Hidden Services}
Good, but as seen in Zooko's triangle we don't have the unique address.
\subsubsection{Squaring Zooko's triangle}
Bitcoin chain

\section{Transport security}
What's wrong with tcp is slow and insecure. How to move away from it? Well, we don't really have any other option to base it on UDP.
But we love reliability!

Issues with too big frames for firewalls?
\section{The {\secit Body} of The Paper}
\section{Conclusions}

@@

\begin{appendix}
Define Perfect forward secrecy

Using Elliptic curve crypto but not backdoored.

Impact on censorship( when encrypted blobs can be transferred)
\section{Final Thoughts}
